
\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\usepackage{setspace}
\usepackage{titlesec}

\titleformat{\section}{\Large\bfseries}{}{0em}{}
\titleformat{\subsection}{\large\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Question Paper}}
\end{center}

\section*{Section A}
\textbf{Instructions:} Answer all questions. Each question carries 1 mark.\\

\begin{enumerate}
    \item What is Newton’s first law of motion? Explain with an example.
    \item How does Newton’s second law help us define the unit of force?
    \item Define the zeroth law of thermodynamics and explain its significance.
    \item Explain the concept of specific heat capacity and its significance in thermodynamics.
    \item Define a circle and explain its basic components.
    \item How do you construct the tangent to a circle from an external point? Explain with steps.
    \item Define a vector and differentiate it from a scalar quantity with examples.
    \item How do you find the unit vector in the direction of a given vector? Explain with an 
example.
    \item Define a matrix and explain its different types with examples.
    \item How do you determine whether a given matrix is invertible? Explain with an example.
\end{enumerate}

\section*{Section B}
\textbf{Instructions:} Answer 5 questions. Each question carries 10 marks. Internal choice is provided.\\

\begin{enumerate}
    \item State and explain Newton’s second law of motion. Derive the mathematical expression 
for force. 

\\\\(OR)\\\\

 Explain the concept of momentum. State and prove the law of conservation of 

momentum.
    \item Compare reversible and irreversible processes in thermodynamics and discuss their 
practical implications. 

\\\\(OR)\\\\

 Derive the expression for the efficiency of a Carnot engine.
    \item Compare and contrast secants and tangents of a circle with their mathematical 
properties. 

\\\\(OR)\\\\

 Derive the equation of a circle in standard form.
    \item Compare and contrast the physical significance of the dot product and the cross 
product. 

\\\\(OR)\\\\

 Derive the formula for the projection of one vector onto another.
    \item Prove that the determinant of a product of two square matrices is equal to the product of 
their determinants. 

\\\\(OR)\\\\

 Derive the characteristic equation of a square matrix and explain its significance.
\end{enumerate}

\end{document}
    